Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
more section 3 edits
Give the game away early in equational theory

Specifications have a theory of equality $\equiv$ as well
as approximation $<:$ which we define here.
%For brevity here we use abbreviations $\term{fwd}$, $\term{bwd}$, and
%$\term{cen}$ for region constants.

@@

The equational theory provides not only an axiomatic semantics
for the language, which the user can use to rewrite their
specification, but it is also used extensively in the inference
procedure (\cref{subsec:inference}) to simplify specifications.

>>>>

Specifications have a theory of equality, $\equiv$, providing axiomatic
semantics for the language. This enables users to rewrite their specification
and helps the inference procedure (\Cref{subsec:inference}) simplify
specifications. Additionally, specifications have a theory of approximation,
$<:$, that can be used by the users to weaken specifications for succintness in
the source.

@@
